Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description

### 2020-05-12 paper/main.tex
different table for nouns rules and counts

A preliminary annotation was performed by one person according to the rules (see
Table XYZ). Minor corrections due to incorrectly applied rules were by the
author.

\begin{table*}[t]
    \caption{Narrator's descriptive nouns.
        All categories sorted alphapetically.
    Examples are given in English.}
\label{tab:descr-nouns-count}
\begin{tabular}{lll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress
shirt \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

% Tabelle der Descriptive Nouns;
\todo[inline]{Caption hübsch machen}

\begin{table*}[t]
    \caption{Narrator's descriptive nouns.
        All categories sorted alphapetically.
    Examples are given in English.}
\label{tab:descr-nouns-count}
\begin{tabular}{llllllllllll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress shirt & \anBodyAll & \anBodyI & \anBodyII & \anBodyIII & \anBodyIV & \anBodyV & \anBodyVI & \anBodyVII & \anBodyVIII \tabularnewline

bodypart & limbs and trousers & arm, finger, leg, toe & \anBodypartAll & \anBodypartI & \anBodypartII & \anBodypartIII & \anBodypartIV & \anBodypartV & \anBodypartVI & \anBodypartVII & \anBodypartVIII \tabularnewline

face & face or parts of it & face, ear, nose, mouth & \anFaceAll & \anFaceI & \anFaceII & \anFaceIII & \anFaceIV & \anFaceV & \anFaceVI & \anFaceVII & \anFaceVIII \tabularnewline

female & female person & nurse, mother, woman & \anFemaleAll & \anFemaleI & \anFemaleII & \anFemaleIII & \anFemaleIV & \anFemaleV & \anFemaleVI & \anFemaleVII & \anFemaleVIII \tabularnewline

females & female persons & women & \anFemalesAll & \anFemalesI & \anFemalesII & \anFemalesIII & \anFemalesIV & \anFemalesV & \anFemalesVI & \anFemalesVII & \anFemalesVIII \tabularnewline

fname & female name & Jenny & \anFnameAll & \anFnameI & \anFnameII & \anFnameIII & \anFnameIV & \anFnameV & \anFnameVI & \anFnameVII & \anFnameVIII \tabularnewline

furniture & movable objects insides/outsides & bench, bed, table, chair & \anFurnitureAll & \anFurnitureI & \anFurnitureII & \anFurnitureIII & \anFurnitureIV & \anFurnitureV & \anFurnitureVI & \anFurnitureVII & \anFurnitureVIII \tabularnewline

geo & immobile landmarks & building, tree, street, alley, meadow, cornfield, river & \anGeoAll & \anGeoI & \anGeoII & \anGeoIII & \anGeoIV & \anGeoV & \anGeoVI & \anGeoVII & \anGeoVIII \tabularnewline

geo-room & rooms / locales; elements defining a locale's spatial layout & living room; wall, door, window, floor, turf & \anGeoroomAll & \anGeoroomI & \anGeoroomII & \anGeoroomIII & \anGeoroomIV & \anGeoroomV & \anGeoroomVI & \anGeoroomVII & \anGeoroomVIII \tabularnewline

head & non-face parts of the head; worn headgear & head, hair, ear, neck, helmet & \anHeadAll & \anHeadI & \anHeadII & \anHeadIII & \anHeadIV & \anHeadV & \anHeadVI & \anHeadVII & \anHeadVIII \tabularnewline

male & male person & man, father, soldier & \anMaleAll & \anMaleI & \anMaleII & \anMaleIII & \anMaleIV & \anMaleV & \anMaleVI & \anMaleVII & \anMaleVIII \tabularnewline

males & male persons & boys, opponents & \anMalesAll & \anMalesI & \anMalesII & \anMalesIII & \anMalesIV & \anMalesV & \anMalesVI & \anMalesVII & \anMalesVIII \tabularnewline

mname & male name & Bubba, Kennedy & \anMnameAll & \anMnameI & \anMnameII & \anMnameIII & \anMnameIV & \anMnameV & \anMnameVI & \anMnameVII & \anMnameVIII \tabularnewline

object & countable entity with firm boundarie & telephone, car & \anObjectAll & \anObjectI & \anObjectII & \anObjectIII & \anObjectIV & \anObjectV & \anObjectVI & \anObjectVII & \anObjectVIII \tabularnewline

objects & countable entities with firm boundaries &  wheels, photos & \anObjectsAll & \anObjectsI & \anObjectsII & \anObjectsIII & \anObjectsIV & \anObjectsV & \anObjectsVI & \anObjectsVII & \anObjectsVIII \tabularnewline

persons & concrete persons of unknown sex / gender & hippies, patients & \anPersonsAll & \anPersonsI & \anPersonsII & \anPersonsIII & \anPersonsIV & \anPersonsV & \anPersonsVI & \anPersonsVII & \anPersonsVIII \tabularnewline

setting\_new & setting mentioned for the first time &  on a ``bridge'', on an ``alley'', on ``campus'' & \anSettingnewAll & \anSettingnewI & \anSettingnewII & \anSettingnewIII & \anSettingnewIV & \anSettingnewV & \anSettingnewVI & \anSettingnewVII & \anSettingnewVIII \tabularnewline

setting\_rec & recurring setting & at the ``bus stop'' & \anSettingrecAll &
\anSettingrecI & \anSettingrecII & \anSettingrecIII & \anSettingrecIV & \anSettingrecV & \anSettingrecVI & \anSettingrecVII & \anSettingrecVIII \tabularnewline
++ & nouns, adverbial adjectives and adverbs & in the ``evening'', it's ``daytime'', ``later'' &  anAll & \anI & \anII & \anIII & \anIV & \anV & \anVI & \anVII & \anVIII \tabularnewline
aDescrV & aDescrVI & aDescrVII & aDescrVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

>>>>

A preliminary annotation was performed by one person according to the rules (see
Table \ref{tab:descr-nouns-rules}). Minor corrections due to incorrectly applied
rules were by the author.

\todo[inline]{so ist die Tabelle zu breit; schrift kleiner oder Text kürzen?
Könnte durchaus auch detaillierteren Text schreiben}

% rules Tabelle für descriptiven nouns
\begin{table*}[t]
    \caption{Descriptive nouns spoken by the audio-description's narrator:
    cateogries, annotation rules and examples (given in English).}
\label{tab:descr-nouns-rules}
\begin{tabular}{lll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress
shirt \tabularnewline
bodypart & limbs and trousers & arm, finger, leg, toe \tabularnewline
face & face or parts of it & face, ear, nose, mouth \tabularnewline
female & female person & nurse, mother, woman \tabularnewline
females & female persons & women \tabularnewline
fname & female name & Jenny \tabularnewline
furniture & moveable objects insides and outsides & bench, bed, table, chair
\tabularnewline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield, river \tabularnewline
geo-room & rooms (insides) or  locales (outsides) & living room; wall, door, window, floor, turf \tabularnewline
head & non-face parts of the head; worn headgear & head, hair, ear, neck,
helmet \tabularnewline
male & male person & man, father, soldier \tabularnewline
males & male persons & boys, opponents \tabularnewline
mname & male name & Bubba, Kennedy \tabularnewline
object & countable entity with firm boundarie & telephone, car \tabularnewline
persons & concrete persons of unknown sex & hippies, patients \tabularnewline
setting\_new & setting mentioned for the first time &  on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
setting\_rec & recurring setting & at the ``bus stop'' \tabularnewline
++ & nouns, adverbial adjectives and adverbs & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline

\bottomrule
\end{tabular}
\end{table*}

% counts Tabelle für descriptiven nouns
\begin{table*}[t]
    \caption{Descriptive nouns spoken by the audio-descriptions narrator:
        counts for the whole audio-only stimulus and its eight segments used
        during fMRI scanning.}
\label{tab:descr-nouns-counts}
\begin{tabular}{llllllllll}
\toprule
\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
\midrule
body & \anBodyAll & \anBodyI & \anBodyII & \anBodyIII & \anBodyIV & \anBodyV & \anBodyVI & \anBodyVII & \anBodyVIII \tabularnewline
bodypart &  \anBodypartAll & \anBodypartI & \anBodypartII & \anBodypartIII & \anBodypartIV & \anBodypartV & \anBodypartVI & \anBodypartVII & \anBodypartVIII \tabularnewline
face & \anFaceAll & \anFaceI & \anFaceII & \anFaceIII & \anFaceIV & \anFaceV & \anFaceVI & \anFaceVII & \anFaceVIII \tabularnewline
female & \anFemaleAll & \anFemaleI & \anFemaleII & \anFemaleIII & \anFemaleIV & \anFemaleV & \anFemaleVI & \anFemaleVII & \anFemaleVIII \tabularnewline
females & \anFemalesAll & \anFemalesI & \anFemalesII & \anFemalesIII & \anFemalesIV & \anFemalesV & \anFemalesVI & \anFemalesVII & \anFemalesVIII \tabularnewline
fname & \anFnameAll & \anFnameI & \anFnameII & \anFnameIII & \anFnameIV & \anFnameV & \anFnameVI & \anFnameVII & \anFnameVIII \tabularnewline
furniture & \anFurnitureAll & \anFurnitureI & \anFurnitureII & \anFurnitureIII & \anFurnitureIV & \anFurnitureV & \anFurnitureVI & \anFurnitureVII & \anFurnitureVIII \tabularnewline
geo & \anGeoAll & \anGeoI & \anGeoII & \anGeoIII & \anGeoIV & \anGeoV & \anGeoVI & \anGeoVII & \anGeoVIII \tabularnewline
geo-room & \anGeoroomAll & \anGeoroomI & \anGeoroomII & \anGeoroomIII & \anGeoroomIV & \anGeoroomV & \anGeoroomVI & \anGeoroomVII & \anGeoroomVIII \tabularnewline
head & \anHeadAll & \anHeadI & \anHeadII & \anHeadIII & \anHeadIV & \anHeadV & \anHeadVI & \anHeadVII & \anHeadVIII \tabularnewline
male & \anMaleAll & \anMaleI & \anMaleII & \anMaleIII & \anMaleIV & \anMaleV & \anMaleVI & \anMaleVII & \anMaleVIII \tabularnewline
males & \anMalesAll & \anMalesI & \anMalesII & \anMalesIII & \anMalesIV & \anMalesV & \anMalesVI & \anMalesVII & \anMalesVIII \tabularnewline
mname & \anMnameAll & \anMnameI & \anMnameII & \anMnameIII & \anMnameIV & \anMnameV & \anMnameVI & \anMnameVII & \anMnameVIII \tabularnewline
object & \anObjectAll & \anObjectI & \anObjectII & \anObjectIII & \anObjectIV & \anObjectV & \anObjectVI & \anObjectVII & \anObjectVIII \tabularnewline
objects & \anObjectsAll & \anObjectsI & \anObjectsII & \anObjectsIII & \anObjectsIV & \anObjectsV & \anObjectsVI & \anObjectsVII & \anObjectsVIII \tabularnewline
persons & \anPersonsAll & \anPersonsI & \anPersonsII & \anPersonsIII & \anPersonsIV & \anPersonsV & \anPersonsVI & \anPersonsVII & \anPersonsVIII \tabularnewline

setting\_new & \anSettingnewAll & \anSettingnewI & \anSettingnewII & \anSettingnewIII & \anSettingnewIV & \anSettingnewV & \anSettingnewVI & \anSettingnewVII & \anSettingnewVIII \tabularnewline

setting\_rec & \anSettingrecAll &
\anSettingrecI & \anSettingrecII & \anSettingrecIII & \anSettingrecIV & \anSettingrecV & \anSettingrecVI & \anSettingrecVII & \anSettingrecVIII \tabularnewline
++ & \anAll & \anI & \anII & \anIII & \anIV & \anV & \anVI & \anVII & \anVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}
